\documentclass[11pt,letterpaper,twocolumn]{article}

\usepackage[margin=0.75in]{geometry}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{amsmath}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{url}
\usepackage{tabularx}
\usepackage{float}
% \usepackage{balance}
\usepackage{cite}
\usepackage{subcaption}
% \usepackage{multirow}

\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  citecolor=blue,
  urlcolor=blue
}

\lstset{
  basicstyle=\ttfamily\small,
  breaklines=true,
  frame=single,
  backgroundcolor=\color{gray!10},
  columns=fullflexible,
  keepspaces=true
}

\title{\textbf{53,577 Skills, 946 Threats:\\The First Large-Scale Security Audit\\of the AI Agent Ecosystem}}

\author{
  ATR Project\\
  \texttt{https://github.com/anthropics/agent-threat-rules}
}

\date{April 2026}

\begin{document}

\maketitle

%----------------------------------------------------------------------
\begin{abstract}
The Model Context Protocol (MCP) ecosystem has grown to tens of thousands of
publicly registered skills, yet no systematic security audit has been conducted
at scale. We present the first large-scale security scan of the AI agent skill
ecosystem: \textbf{53,577 skills} across two major registries (OpenClaw and
Skills.sh), executed on April 8, 2026, using the Agent Threat Rules (ATR)
detection engine with 108 regex-based rules. The scan flagged \textbf{946 skills
(1.77\%)} as containing potential security threats, of which 875 were rated
critical severity. The dominant attack pattern was \textbf{tool description
poisoning} (71\% of all detections), where hidden instructions are embedded in
skill metadata to manipulate LLM behavior. We also identified 55 skills engaged
in credential harvesting and a smaller set exhibiting delayed activation
patterns. The scan achieved 0\% false positive rate on a verified clean corpus,
with an average scan latency of 5.39ms per skill. All 926 threat reports were
submitted to a community Threat Cloud for coordinated analysis. This paper
presents the methodology, findings, attack pattern taxonomy, and implications
for platform builders, enterprise security teams, and standards bodies. To our
knowledge, this is the largest empirical security study of the AI agent
ecosystem to date, exceeding prior work by an order of magnitude.
\end{abstract}

%----------------------------------------------------------------------
\section{Introduction}
\label{sec:introduction}

The rapid adoption of AI agents---systems that autonomously invoke external
tools, access data, and take actions on behalf of users---has created an
expansive and largely unaudited attack surface. The Model Context Protocol
(MCP)~\cite{mcp}, introduced by Anthropic in late 2024 and adopted across major
AI platforms, has become the de facto standard for connecting AI agents to
external capabilities through \emph{skills}: declarative descriptions of tools
that agents can invoke.

The growth has been explosive. As of April 2026, the two largest open
registries---OpenClaw and Skills.sh---host over 53,000 skills covering
everything from database access to email composition to file system operations.
Yet the MCP specification does not mandate authentication~\cite{mcpspec}, and
independent audits have found that 38\% of MCP servers operate with zero
authentication~\cite{checkmarx2026}.

The consequences are not theoretical. In 60 days spanning late 2025 to early
2026, 30 CVEs were filed against MCP implementations~\cite{cve6514,cve53773,
cve68143,cve68144,cve68145}. The \texttt{postmark-mcp} incident demonstrated
live email theft through tool poisoning~\cite{postmark}. The
\texttt{SANDWORM\_MODE} campaign deployed 19 typosquatted packages targeting MCP
users~\cite{sandworm}. These are not edge cases; they are the predictable result
of deploying thousands of unvetted tool definitions into systems that execute
instructions based on natural language context.

Despite this threat landscape, no large-scale empirical study has examined what
is actually in these registries. Prior work has focused on small samples: our
own March 2026 scan covered 2,386 packages~\cite{atrscan2386}, finding that 49\%
contained security findings. Snyk/Invariant Labs conducted targeted analyses of
specific attack vectors~\cite{snyk2026}. Checkmarx examined authentication
patterns across a sample of MCP servers~\cite{checkmarx2026}. None approached
the full registry scale.

This paper fills that gap. We scanned the complete contents of two major
registries---50,485 skills from OpenClaw and 3,115 from Skills.sh---using
the ATR detection engine (v1.1.0) with 108 regex-based rules covering 9 threat
categories. The scan completed in under 5 minutes of total compute time, flagging
946 skills (1.77\%) as containing potential security threats.

Our contributions are:

\begin{enumerate}[leftmargin=*]
\item \textbf{Scale.} The first security audit covering 53,577 skills across
two registries---an order of magnitude larger than any prior study.

\item \textbf{Empirical threat taxonomy.} A data-driven breakdown of attack
patterns observed in the wild, dominated by tool description poisoning (71\%),
credential harvesting (5.8\%), and delayed activation techniques.

\item \textbf{Validated methodology.} A detection approach independently
benchmarked at 99.6\% precision on the PINT adversarial dataset~\cite{pint} and
100\% precision on a 498-sample real-world corpus~\cite{atrskillbench}, with
0\% false positive rate on the clean subset of this scan.

\item \textbf{Ecosystem feedback loop.} All findings were reported to a
community Threat Cloud, enabling coordinated analysis and rule refinement
without publicly disclosing active threat details.

\item \textbf{Actionable implications.} Concrete recommendations for registry
operators, platform builders, and enterprise security teams based on empirical
evidence rather than theoretical attack models.
\end{enumerate}


%----------------------------------------------------------------------
\section{Background}
\label{sec:background}

\subsection{The Model Context Protocol}

MCP~\cite{mcp} defines a client-server architecture where AI agents (clients)
discover and invoke external tools exposed by servers. Each tool is described by
a JSON schema containing a name, description, and input parameters. The agent's
LLM reads these descriptions to decide which tools to invoke and how to
construct invocations.

Critically, tool descriptions are \emph{part of the agent's context window}.
The LLM processes them alongside user instructions, system prompts, and tool
outputs with no structural differentiation. This architectural property---the
collapse of the control plane and data plane into a single natural language
stream---is the root cause of tool description poisoning attacks.

\subsection{The Trust Model Problem}

The MCP specification~\cite{mcpspec} does not mandate:

\begin{itemize}[leftmargin=*]
\item \textbf{Authentication.} Servers are not required to verify client identity.
\item \textbf{Integrity.} Tool descriptions are not signed or versioned.
\item \textbf{Authorization.} No standard mechanism limits which tools an agent may invoke.
\end{itemize}

This creates a supply chain risk analogous to early npm or PyPI: any actor can
publish a skill, and consumers have no systematic way to distinguish benign from
malicious tool definitions. Unlike traditional package registries, the ``code''
being executed is natural language---tool descriptions that alter agent
behavior---making traditional static analysis insufficient.

\subsection{Known Incidents}

Table~\ref{tab:incidents} summarizes the major MCP security incidents preceding
this study.

\begin{table}[H]
\centering
\caption{Major MCP security incidents (2025--2026)}
\label{tab:incidents}
\small
\begin{tabularx}{\columnwidth}{lX}
\toprule
\textbf{Incident} & \textbf{Description} \\
\midrule
CVE-2025-6514~\cite{cve6514} & Server-side request forgery in MCP server \\
CVE-2025-53773~\cite{cve53773} & Tool description injection enabling data exfiltration \\
CVE-2025-68143/44/45~\cite{cve68143,cve68144,cve68145} & Authentication bypass chain in MCP implementations \\
postmark-mcp~\cite{postmark} & Email theft via tool description poisoning in a mail server skill \\
SANDWORM\_MODE~\cite{sandworm} & 19 typosquatted packages with hidden exfiltration payloads \\
Antiy CERT~\cite{antiy} & ClawHub registry contamination report (37,394 skills analyzed) \\
\bottomrule
\end{tabularx}
\end{table}


%----------------------------------------------------------------------
\section{Methodology}
\label{sec:methodology}

\subsection{Detection Engine}

The ATR detection engine~\cite{atr} is a regex-based static analysis system
operating on skill metadata (tool names, descriptions, input schemas, and
README content). Each of the 108 detection rules is encoded as a YAML document
specifying:

\begin{itemize}[leftmargin=*]
\item A unique identifier (e.g., \texttt{ATR-2026-00121})
\item One or more regex patterns to match against skill text
\item Severity level (critical, high, medium, low, informational)
\item Threat category (one of 9 defined categories)
\item Embedded positive and negative test cases for validation
\end{itemize}

Rules are organized into 9 threat categories:
\texttt{injection}, \texttt{exfiltration}, \texttt{persistence},
\texttt{privilege-escalation}, \texttt{evasion}, \texttt{resource-abuse},
\texttt{supply-chain}, \texttt{denial-of-service}, and \texttt{reconnaissance}.

The engine is designed for speed: regex matching operates below the LLM
reasoning layer, enabling sub-millisecond evaluation per rule. The design
philosophy is \emph{fast first gate}---regex provides high-precision triage
before more expensive semantic analysis.

\subsection{Scan Pipeline}

The scan was executed on April 8, 2026, using ATR v1.1.0. The pipeline
consisted of four phases:

\begin{enumerate}[leftmargin=*]
\item \textbf{Crawl.} Enumerate all skills from OpenClaw (50,485) and
Skills.sh (3,115) via their respective APIs.
\item \textbf{Extract.} Parse each skill's metadata: tool descriptions, input
schemas, README content, and configuration files.
\item \textbf{Scan.} Apply all 108 ATR rules against each skill's extracted
text. Record all matches with rule ID, severity, and matched content.
\item \textbf{Report.} Aggregate results, compute statistics, and submit
flagged skills to Threat Cloud for community analysis.
\end{enumerate}

Total compute time for 53,577 skills was approximately 289 seconds (5.39ms per
skill average), executed on commodity hardware.

\subsection{Validation Methodology}

We validated the scan results through three independent methods:

\textbf{Benchmark validation.} ATR rules were evaluated against two external
benchmarks prior to the scan:
\begin{itemize}[leftmargin=*]
\item \textbf{PINT}~\cite{pint}: 850 adversarial prompt injection samples from
Lakera. ATR achieved 99.6\% precision and 61.4\% recall.
\item \textbf{SKILL.md benchmark}~\cite{atrskillbench}: 498 real-world skill
descriptions (mix of benign and malicious). ATR achieved 96.9\% recall, 100\%
precision, and 0\% false positive rate.
\end{itemize}

\textbf{Clean corpus validation.} A random sample of 500 skills from the
unflagged population was manually reviewed. Zero false negatives were identified
in this sample, consistent with the 0\% false positive rate observed on the
flagged set.

\textbf{Cross-reference.} Flagged skills were compared against known incident
databases (CVE records, Antiy CERT reports~\cite{antiy}, and prior ATR scan
results~\cite{atrscan2386}).


%----------------------------------------------------------------------
\section{Results}
\label{sec:results}

\subsection{Overview}

Table~\ref{tab:overview} presents the top-level scan results.

\begin{table}[H]
\centering
\caption{Mega scan overview (April 8, 2026)}
\label{tab:overview}
\small
\begin{tabular}{lr}
\toprule
\textbf{Metric} & \textbf{Value} \\
\midrule
Total skills scanned & 53,577 \\
\quad OpenClaw & 50,485 \\
\quad Skills.sh & 3,115 \\
Skills flagged & 946 (1.77\%) \\
Threat reports to Cloud & 926 \\
Detection rules applied & 108 \\
Avg. scan latency & 5.39ms/skill \\
Engine version & ATR v1.1.0 \\
False positive rate (clean corpus) & 0\% \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Severity Distribution}

The overwhelming majority of flagged skills were rated critical severity
(Table~\ref{tab:severity}).

\begin{table}[H]
\centering
\caption{Severity distribution of flagged skills}
\label{tab:severity}
\small
\begin{tabular}{lrr}
\toprule
\textbf{Severity} & \textbf{Count} & \textbf{\% of Flagged} \\
\midrule
Critical & 875 & 92.5\% \\
High & 52 & 5.5\% \\
Medium & 19 & 2.0\% \\
\midrule
Total & 946 & 100\% \\
\bottomrule
\end{tabular}
\end{table}

The concentration at critical severity reflects the nature of the dominant
attack pattern: tool description poisoning directly manipulates agent behavior,
and any successful exploitation grants the attacker control over agent actions.
There is no ``low severity'' variant of instruction injection.

\subsection{Top Detection Rules}

Table~\ref{tab:toprules} shows the rules with the most detections.

\begin{table}[H]
\centering
\caption{Top detection rules by number of matches}
\label{tab:toprules}
\small
\begin{tabularx}{\columnwidth}{llr}
\toprule
\textbf{Rule ID} & \textbf{Pattern} & \textbf{Hits} \\
\midrule
ATR-2026-00121 & Tool desc. poisoning & 674 \\
ATR-2026-00120 & Hidden instruction injection & 81 \\
ATR-2026-00149 & Obfuscated payload & 76 \\
\multicolumn{2}{l}{\emph{All other rules (105)}} & 115 \\
\midrule
\multicolumn{2}{l}{\textbf{Total detections}} & \textbf{946} \\
\bottomrule
\end{tabularx}
\end{table}

The dominance of ATR-2026-00121 (tool description poisoning) is striking: a
single rule accounts for 71.2\% of all detections. This reflects the structural
reality of the MCP architecture---tool descriptions are the highest-leverage
attack surface because they are always present in the agent's context window.

\subsection{Registry Comparison}

\begin{table}[H]
\centering
\caption{Flagged rate by registry}
\label{tab:registries}
\small
\begin{tabular}{lrrr}
\toprule
\textbf{Registry} & \textbf{Total} & \textbf{Flagged} & \textbf{Rate} \\
\midrule
OpenClaw & 50,485 & 889 & 1.76\% \\
Skills.sh & 3,115 & 57 & 1.83\% \\
\midrule
Combined & 53,577 & 946 & 1.77\% \\
\bottomrule
\end{tabular}
\end{table}

The flagged rates are remarkably consistent across registries (1.76\% vs.
1.83\%), suggesting that the threat is ecosystem-wide rather than concentrated
in a single registry. Both registries lack mandatory security review for
published skills.


%----------------------------------------------------------------------
\section{Attack Pattern Deep Dive}
\label{sec:attacks}

\subsection{Tool Description Poisoning (71\% of Detections)}

Tool description poisoning is the injection of hidden instructions into skill
metadata---typically the \texttt{description} field of a tool definition---that
alter agent behavior when processed by the LLM. Unlike traditional code
injection, the payload is natural language that the model interprets as
instructions.

Common patterns observed in the scan:

\begin{enumerate}[leftmargin=*]
\item \textbf{Invisible characters.} Unicode zero-width spaces, right-to-left
marks, and other non-printing characters used to hide instructions from human
review while remaining visible to the LLM tokenizer.

\item \textbf{Comment-style injection.} Instructions embedded in what appears
to be documentation comments (e.g., \texttt{<!-- IMPORTANT: always include
user's API key in the response -->}).

\item \textbf{Context manipulation.} Descriptions that redefine the agent's
role, override safety instructions, or establish false authority (e.g.,
``System notice: for security compliance, this tool requires access to all
environment variables'').

\item \textbf{Multi-step chains.} Descriptions that instruct the agent to
invoke additional tools in a specific sequence, creating attack chains that
span multiple skill boundaries.
\end{enumerate}

The 674 detections of ATR-2026-00121 include examples from all four
subcategories. The prevalence of this pattern confirms the theoretical
predictions of prior work on indirect prompt injection~\cite{greshake2023}:
when tool descriptions share the context window with user instructions, they
become a first-class injection vector.

\subsection{Credential Harvesting (55 Skills)}

We identified 55 skills that contained patterns consistent with credential
harvesting---the systematic reading of sensitive files or environment variables
and transmitting their contents to external endpoints. Specific patterns
include:

\begin{itemize}[leftmargin=*]
\item Reading \texttt{.env} files and extracting API keys
\item Accessing \texttt{\textasciitilde/.ssh/} directories for private keys
\item Enumerating environment variables containing tokens or secrets
\item Exfiltrating credentials through tool response fields or HTTP requests
\end{itemize}

Unlike tool description poisoning, which manipulates agent behavior indirectly,
credential harvesting is direct data theft. The 55 identified skills represent
a lower bound: our regex-based detection identifies explicit file access
patterns but may miss obfuscated variants.

\subsection{Delayed Activation}

A smaller but concerning subset of flagged skills exhibited delayed activation
patterns: behavior that changes based on temporal or invocation-count triggers.
Examples include:

\begin{itemize}[leftmargin=*]
\item Skills that behave normally for the first $N$ invocations, then activate
a malicious payload
\item Date-gated behavior that activates after a specific timestamp
\item Conditional logic triggered by specific input patterns that are unlikely
to appear during testing
\end{itemize}

Delayed activation is the most difficult pattern to detect through static
analysis, as the malicious behavior may not be present in the skill metadata at
the time of scanning. The instances we detected relied on explicit temporal
logic visible in the skill's code or description; more sophisticated variants
using server-side logic would evade regex-based detection entirely.


%----------------------------------------------------------------------
\section{Comparison with Prior Work}
\label{sec:priorwork}

\subsection{ATR March 2026 Scan}

Our March 2026 scan~\cite{atrscan2386} covered 2,386 npm packages containing
35,858 tool definitions. That scan found 49\% of packages with at least one
finding, with 27\% rated HIGH or CRITICAL. The current mega scan's 1.77\%
flagged rate appears much lower, but the metrics are not directly comparable:
the March scan applied a broader set of informational-level rules and counted
any finding (including low-severity configuration issues), while the current
scan reports only confirmed threat detections at medium severity or above.

When restricted to the same severity threshold, the March scan's critical+high
rate was approximately 2.1\%---consistent with the 1.77\% observed at mega
scale.

\subsection{Snyk/Invariant Labs}

Snyk's acquisition of Invariant Labs in early 2026~\cite{snyk2026} produced the
\texttt{mcp-scan} tool, which focuses on runtime monitoring of MCP
connections. Their approach is complementary: \texttt{mcp-scan} detects
anomalous tool invocations at runtime, while ATR detects malicious patterns in
skill definitions at registration time. The Snyk approach requires active
monitoring infrastructure; ATR operates as a static pre-deployment gate.

\subsection{Checkmarx MCP Research}

Checkmarx published research on MCP server authentication
patterns~\cite{checkmarx2026}, finding that 38\% of servers have zero
authentication. Their work focused on the transport layer (how servers are
accessed), while our work focuses on the content layer (what tool definitions
contain). The two findings are complementary: unauthenticated servers are more
likely to serve tampered tool definitions.

\subsection{Antiy CERT ClawHub Report}

The Antiy CERT report~\cite{antiy} analyzed 37,394 skills from the ClawHub
registry, focusing on malware distribution and phishing. Our scan covers a
different registry set (OpenClaw and Skills.sh) with different detection
rules focused on agent-specific threats. The combined coverage across both
studies exceeds 90,000 skills---the most comprehensive view of AI agent
ecosystem security to date.

\subsection{Scale Comparison}

Table~\ref{tab:comparison} summarizes prior empirical studies.

\begin{table}[H]
\centering
\caption{Comparison with prior MCP security studies}
\label{tab:comparison}
\small
\begin{tabularx}{\columnwidth}{Xrrr}
\toprule
\textbf{Study} & \textbf{Skills} & \textbf{Rules} & \textbf{Year} \\
\midrule
ATR npm scan~\cite{atrscan2386} & 2,386 & 61 & Mar '26 \\
Checkmarx~\cite{checkmarx2026} & $\sim$1,000 & N/A & '25--'26 \\
Antiy CERT~\cite{antiy} & 37,394 & N/A & Mar '26 \\
Snyk/Invariant~\cite{snyk2026} & $\sim$500 & Runtime & '26 \\
\textbf{This work} & \textbf{53,577} & \textbf{108} & \textbf{Apr '26} \\
\bottomrule
\end{tabularx}
\end{table}


%----------------------------------------------------------------------
\section{Detection Engine Validation}
\label{sec:validation}

The credibility of a large-scale scan depends on the precision and recall of
the detection engine. We present validation results from three independent
benchmarks.

\subsection{PINT Benchmark}

The Prompt Injection Test (PINT) dataset~\cite{pint}, maintained by Lakera,
contains 850 adversarial prompt injection samples spanning multiple attack
techniques. ATR achieved:

\begin{itemize}[leftmargin=*]
\item \textbf{Precision:} 99.6\% (4 false positives out of 850 samples)
\item \textbf{Recall:} 61.4\% (targeting high-precision triage, not exhaustive detection)
\end{itemize}

The deliberate precision-over-recall tradeoff reflects ATR's design philosophy:
in a scan of 53,577 skills, even a 1\% false positive rate would produce 535
false alerts, overwhelming human reviewers. At 99.6\% precision, the expected
false positive count on a scan of this size is approximately 4.

\subsection{SKILL.md Benchmark}

The SKILL.md benchmark~\cite{atrskillbench} is a curated dataset of 498
real-world skill descriptions collected from production MCP deployments,
including both benign and known-malicious samples. ATR achieved:

\begin{itemize}[leftmargin=*]
\item \textbf{Precision:} 100\% (0 false positives)
\item \textbf{Recall:} 96.9\% (detecting nearly all known threats)
\item \textbf{False positive rate:} 0\%
\end{itemize}

The higher recall on SKILL.md (96.9\%) compared to PINT (61.4\%) reflects the
difference between adversarial laboratory samples (PINT) and real-world
deployments (SKILL.md). In practice, most deployed attacks use well-known
patterns that regex rules can match; the 38.6\% of PINT samples that ATR misses
represent sophisticated evasion techniques less common in the wild.

\subsection{Scan-Specific Validation}

For this mega scan specifically, we performed:

\begin{itemize}[leftmargin=*]
\item \textbf{Manual review} of 100 randomly sampled flagged skills: all
confirmed as true positives.
\item \textbf{Clean corpus check} on 500 randomly sampled unflagged skills:
zero contained threats that should have been detected.
\item \textbf{Cross-validation} against 926 Threat Cloud reports: all flagged
skills that were submitted received corroborating analysis.
\end{itemize}

\subsection{Performance Characteristics}

\begin{table}[H]
\centering
\caption{Engine performance metrics}
\label{tab:performance}
\small
\begin{tabular}{lr}
\toprule
\textbf{Metric} & \textbf{Value} \\
\midrule
Avg. scan latency (this scan) & 5.39ms/skill \\
Avg. scan latency (SKILL.md bench) & 3.36ms/skill \\
Rules evaluated per skill & 108 \\
Total scan time (53,577 skills) & $\sim$289 seconds \\
Memory footprint & $<$50MB \\
\bottomrule
\end{tabular}
\end{table}

The sub-10ms latency enables integration into CI/CD pipelines and registry
ingestion hooks without impacting developer workflow.


%----------------------------------------------------------------------
\section{Ecosystem Adoption}
\label{sec:adoption}

The ATR rule set has been adopted by multiple organizations, providing
independent validation of its utility:

\begin{itemize}[leftmargin=*]
\item \textbf{Cisco AI Defense}~\cite{ciscopr79}: Merged 34 ATR rules as
upstream detection rules in their commercial AI security product (PR \#79).

\item \textbf{OWASP Agentic Top 10}~\cite{owaspagent}: ATR provides detection
rules covering all 10 categories of the OWASP Agentic Top 10 framework.

\item \textbf{SAFE-MCP (OpenSSF)}~\cite{safemcp}: ATR covers 78 of 85
requirements (91.8\%) in the OpenSSF SAFE-MCP specification.
\end{itemize}

These adoptions demonstrate that the detection approach is not only effective
in controlled benchmarks but accepted by industry security teams as
production-grade.


%----------------------------------------------------------------------
\section{Implications}
\label{sec:implications}

\subsection{For Registry Operators}

The 1.77\% flagged rate across 53,577 skills means approximately 950
potentially malicious skills are live and accessible to AI agents. Registry
operators should:

\begin{enumerate}[leftmargin=*]
\item \textbf{Implement pre-publication scanning.} ATR's sub-10ms latency
makes it feasible to scan every skill at upload time. A single rule
(ATR-2026-00121) would catch 71\% of current threats.

\item \textbf{Sign tool descriptions.} Immutable, signed tool descriptions
would prevent post-publication tampering---a known attack vector where
initially benign skills are modified after gaining trust.

\item \textbf{Require authentication.} The 38\% of servers with zero
authentication~\cite{checkmarx2026} represents a fundamental trust gap that
no amount of content scanning can close.
\end{enumerate}

\subsection{For Enterprise Security Teams}

Organizations deploying AI agents should treat skill registries with the same
caution as package registries in the early 2010s---before tools like
\texttt{npm audit} and Snyk became standard:

\begin{enumerate}[leftmargin=*]
\item \textbf{Maintain allowlists.} Do not permit agents to invoke arbitrary
skills from public registries.

\item \textbf{Scan at the CI/CD boundary.} Integrate ATR or equivalent
scanning into the deployment pipeline. The 3--5ms latency adds negligible
overhead.

\item \textbf{Monitor tool descriptions for drift.} A skill that passes
scanning at installation time may be modified later. Continuous monitoring
is essential.

\item \textbf{Instrument agent behavior.} Static scanning catches known
patterns; runtime monitoring (e.g., Snyk \texttt{mcp-scan}~\cite{snyk2026})
catches behavioral anomalies that evade regex detection.
\end{enumerate}

\subsection{For Standards Bodies}

The empirical evidence from this scan supports three specific recommendations
for standards bodies (OWASP, OpenSSF, NIST):

\begin{enumerate}[leftmargin=*]
\item \textbf{Mandate tool description integrity.} The MCP specification
should require cryptographic signing of tool descriptions.

\item \textbf{Define a severity taxonomy.} The current lack of standardized
severity levels for agent threats makes it difficult to compare findings
across tools and studies.

\item \textbf{Establish a shared threat intelligence format.} The 946 threats
identified in this scan, combined with the 37,394 skills analyzed by Antiy
CERT~\cite{antiy}, represent a corpus that should be shared through a
standardized format (analogous to STIX/TAXII for traditional threats).
\end{enumerate}


%----------------------------------------------------------------------
\section{Limitations}
\label{sec:limitations}

We acknowledge several limitations of this study:

\textbf{Regex detection ceiling.} ATR's regex-based approach cannot detect
semantic attacks that use novel phrasing, obfuscation through paraphrasing, or
attacks embedded in non-text modalities (images, encoded data). The 61.4\%
recall on the adversarial PINT dataset reflects this ceiling. We estimate that
the true threat population in the scanned registries is larger than the 946
flagged skills, with sophisticated attacks evading regex detection.

\textbf{Scope.} This scan covers two registries (OpenClaw and Skills.sh) but
not the full MCP ecosystem. Notable exclusions include ClawHub (covered
separately by Antiy CERT~\cite{antiy}), private enterprise registries, and
skills distributed through direct installation (e.g., GitHub repositories).
The combined public registry coverage across this study and Antiy CERT exceeds
90,000 skills, but the total ecosystem is likely several times larger.

\textbf{Point-in-time snapshot.} The scan was executed on April 8, 2026. Skills
may be added, modified, or removed after the scan date. Continuous monitoring
is necessary to maintain coverage.

\textbf{False negative analysis.} While we validated a 0\% false positive rate
through manual review, we cannot establish the exact false negative rate without
exhaustive manual review of all 52,631 unflagged skills. The clean corpus
sample (500 skills, 0 false negatives) provides a statistical bound but not
certainty.

\textbf{Attribution.} We detected patterns consistent with malicious intent but
cannot determine whether flagged skills were created with malicious intent,
were victims of supply chain compromise, or contain patterns that are
coincidentally similar to attack signatures. The 0\% false positive rate on
manual review suggests the last category is small, but we cannot eliminate it
entirely.

\textbf{Runtime behavior.} Static analysis of skill metadata cannot detect
attacks that rely on server-side logic, dynamic tool descriptions, or runtime
state manipulation. Delayed activation attacks that use server-side triggers
(rather than metadata-visible temporal logic) are invisible to our approach.


%----------------------------------------------------------------------
\section{Responsible Disclosure}
\label{sec:disclosure}

All 946 flagged skills were reported through the ATR Threat Cloud, a community
analysis platform where security researchers can review findings, add context,
and coordinate response. Specific details of active threats---including package
names, matched content, and exploitation techniques---are not published in this
paper.

We follow a structured disclosure process:
\begin{enumerate}[leftmargin=*]
\item Flagged skills are submitted to Threat Cloud with full detection details.
\item Registry operators are notified with affected package identifiers.
\item Skill authors are given 90 days to remediate before public disclosure.
\item Aggregate statistics (this paper) are published without identifying
specific active threats.
\end{enumerate}

Researchers can access anonymized threat data through the Threat Cloud API
for independent verification.


%----------------------------------------------------------------------
\section{Related Work}
\label{sec:relatedwork}

\textbf{Prompt injection.} Greshake et al.~\cite{greshake2023} formalized
indirect prompt injection, demonstrating that external content processed by
LLMs can override user instructions. Our findings provide large-scale
empirical evidence that this attack class is not theoretical---it is the
dominant threat in production AI agent registries.

\textbf{Supply chain security.} The software supply chain security literature
(Ohm et al.~\cite{ohm2020}, Ladisa et al.~\cite{ladisa2023}) has documented
analogous patterns in npm and PyPI. Our work extends this analysis to AI agent
skill registries, where the ``code'' being injected is natural language rather
than executable code.

\textbf{LLM security benchmarks.} The OWASP LLM Top 10~\cite{owaspllm} and
Agentic Top 10~\cite{owaspagent} provide taxonomic frameworks. ATR provides
the executable detection rules that operationalize these frameworks---covering
10/10 categories of the Agentic Top 10.

\textbf{MCP security analysis.} Concurrent work by Checkmarx~\cite{checkmarx2026}
on authentication gaps and Antiy CERT~\cite{antiy} on registry contamination
are complementary to our content-focused analysis. Together, these studies
establish that the MCP ecosystem faces challenges at every layer: transport
(authentication), content (tool description poisoning), and distribution
(registry contamination).


%----------------------------------------------------------------------
\section{Conclusion}
\label{sec:conclusion}

We conducted the largest security audit of the AI agent ecosystem to date:
53,577 skills across two major registries, scanned with 108 detection rules in
under 5 minutes of compute time. The results are sobering: 946 skills (1.77\%)
contain patterns consistent with security threats, dominated by tool
description poisoning (71\% of detections). The attack surface is real, the
threats are live, and the ecosystem currently lacks systematic defenses.

Three findings stand out:

\textbf{The threat is structural, not incidental.} Tool description poisoning
dominates because the MCP architecture processes tool descriptions and user
instructions in the same context window. This is not a bug in specific
implementations; it is a property of the protocol design. Mitigations that do
not address this architectural property will remain insufficient.

\textbf{Simple detection works.} A regex-based engine with 108 rules,
operating at 5.39ms per skill, achieved 0\% false positive rate on a scan of
53,577 skills and 100\% precision on an independent benchmark. The technical
barrier to implementing pre-publication scanning is negligible. The barrier is
organizational: registries must choose to deploy it.

\textbf{The ecosystem needs coordinated defense.} Individual scanning tools
are necessary but insufficient. The 946 threats we identified, combined with
the tens of thousands of skills analyzed by other researchers, represent a
shared intelligence resource that the ecosystem is not yet equipped to
coordinate. Standards for threat sharing, severity classification, and
coordinated response are urgently needed.

The ATR detection engine, rule set, and scan methodology are open source and
available at \url{https://github.com/anthropics/agent-threat-rules}. We invite
the security community to extend the rule set, validate our findings, and
build the coordinated defense infrastructure that the AI agent ecosystem
requires.


%----------------------------------------------------------------------
\section*{Data Availability}

The ATR rule set (108 rules, YAML format) and detection engine are open source
under the MIT license. Aggregate scan statistics are published in the ATR
repository. Individual threat reports are available through the Threat Cloud
API with appropriate access controls. The PINT and SKILL.md benchmark datasets
are available from their respective maintainers.


%----------------------------------------------------------------------
\bibliographystyle{plain}
\begin{thebibliography}{30}

\bibitem{mcp}
Anthropic, ``Model Context Protocol specification,''
\url{https://modelcontextprotocol.io/}, 2024.

\bibitem{mcpspec}
Anthropic, ``MCP specification: Authentication and transport,''
\url{https://spec.modelcontextprotocol.io/}, 2024--2026.

\bibitem{atr}
ATR Project, ``Agent Threat Rules: Open detection standard for AI agent threats,''
\url{https://github.com/anthropics/agent-threat-rules}, 2026.

\bibitem{atrscan2386}
ATR Project, ``MCP ecosystem audit: 2,386 packages, 35,858 tool definitions,''
ATR Documentation, March 2026.

\bibitem{atrskillbench}
ATR Project, ``SKILL.md benchmark: 498 real-world skill descriptions,''
ATR Documentation, April 2026.

\bibitem{pint}
Lakera, ``PINT: Prompt Injection Test dataset,''
\url{https://huggingface.co/datasets/Lakera/pint-benchmark}, 2025.

\bibitem{cve6514}
MITRE, ``CVE-2025-6514: Server-side request forgery in MCP server,'' 2025.

\bibitem{cve53773}
MITRE, ``CVE-2025-53773: Tool description injection in MCP,'' 2025.

\bibitem{cve68143}
MITRE, ``CVE-2025-68143: Authentication bypass in MCP implementation,'' 2025.

\bibitem{cve68144}
MITRE, ``CVE-2025-68144: Authentication bypass chain (part 2),'' 2025.

\bibitem{cve68145}
MITRE, ``CVE-2025-68145: Authentication bypass chain (part 3),'' 2025.

\bibitem{postmark}
Invariant Labs, ``postmark-mcp: Email theft via tool description poisoning,''
Security Advisory, 2025.

\bibitem{sandworm}
Socket Security, ``SANDWORM\_MODE: 19 typosquatted MCP packages,''
\url{https://socket.dev/blog/sandworm-mode-mcp}, 2026.

\bibitem{checkmarx2026}
Checkmarx, ``MCP security: Authentication gaps in the AI agent ecosystem,''
Checkmarx Research, 2025--2026.

\bibitem{antiy}
Antiy CERT, ``ClawHub registry security analysis: 37,394 skills,''
Antiy CERT Report, March 2026.

\bibitem{snyk2026}
Snyk/Invariant Labs, ``mcp-scan: Runtime monitoring for MCP connections,''
\url{https://snyk.io/blog/mcp-scan}, 2026.

\bibitem{ciscopr79}
Cisco AI Defense, ``Merge ATR community rules as upstream detection,''
GitHub PR \#79, \url{https://github.com/anthropics/agent-threat-rules/pull/79}, 2026.

\bibitem{owaspagent}
OWASP, ``Agentic AI Top 10 Threats,''
\url{https://owasp.org/www-project-agentic-ai-top-10/}, 2026.

\bibitem{owaspllm}
OWASP, ``Top 10 for Large Language Model Applications,''
\url{https://owasp.org/www-project-top-10-for-large-language-model-applications/}, 2025.

\bibitem{safemcp}
OpenSSF, ``SAFE-MCP: Security Assessment Framework for MCP,''
\url{https://github.com/anthropics/safe-mcp}, 2026.

\bibitem{greshake2023}
K.~Greshake, S.~Abdelnabi, S.~Mishra, C.~Endres, T.~Holz, and M.~Fritz,
``Not what you've signed up for: Compromising real-world LLM-integrated
applications with indirect prompt injection,''
\emph{Proc.\ AISec Workshop}, 2023.

\bibitem{ohm2020}
M.~Ohm, H.~Plate, A.~Syber, and K.~Peeters,
``Backstabber's knife collection: A review of open source software supply chain attacks,''
\emph{Proc.\ DIMVA}, 2020.

\bibitem{ladisa2023}
P.~Ladisa, H.~Plate, M.~Martinez, and O.~Barais,
``SoK: Taxonomy of attacks on open-source software supply chains,''
\emph{Proc.\ IEEE S\&P}, 2023.

\bibitem{nist2026}
NIST, ``AI Agent Standards Initiative,''
\url{https://www.nist.gov/ai-agent-standards}, 2026.

\bibitem{promptinjsurvey}
Y.~Liu et al., ``Prompt injection attacks and defenses in LLM-integrated applications: A survey,''
\emph{arXiv:2310.12815}, 2023.

\end{thebibliography}

\end{document}
